Predicting trends in the quality of state-of-the-art neural networks without access to training or testing data

### 2020-12-30 submission/NatCom_all_models.tex
putting placehodlers in appendix

We summarize results from a large-scale analysis of hundreds of publicly-available  models.
This broader analysis on a much larger set of CV and NLP models, with a more diverse set of architectures, and developed for a wider range of tasks, complements the previous more detailed analysis on CV and NLP models.
See the Supplementary Information
%~\ref{sxn:appendix} 
for details.
To quantify the relationship between quality metrics and the reported test error and/or accuracy metrics, we use ordinary least squares (similar results are seen with rank correlation metrics) to regress the metrics on the Top1 (and Top5) reported errors (as dependent variables).
These include Top5 errors for the ImageNet-1K model, percent error for the CIFAR-10/100, SVHN, CUB-200-2011 models, and Pixel accuracy (Pix.Acc.) and Intersection-Over-Union (IOU) for other models.
We regress them individually on each of the norm-based and PL-based metrics.

>>>>

We have performed a large-scale analysis of hundreds of publicly-available models.
This broader analysis is on a much larger set of CV and NLP models, with a more diverse set of architectures, that have been developed for a wider range of tasks; and it complements the previous more detailed analysis on CV and NLP models, where we have analyzed only a single architecture series at a time.
See the Supplementary Information
%~\ref{sxn:appendix} 
(and our publicly-available repo)
for details.
To quantify the relationship between quality metrics and the reported test error and/or accuracy metrics, we use ordinary least squares (similar results are seen with rank correlation metrics) to regress the metrics on the Top1 (and Top5) reported errors (as dependent variables).
These include Top5 errors for the ImageNet-1K model, percent error for the CIFAR-10/100, SVHN, CUB-200-2011 models, and Pixel accuracy (Pix.Acc.) and Intersection-Over-Union (IOU) for other models.
We regress them individually on each of the norm-based and PL-based metrics.

### 2020-12-30 submission/NatCom_appendix.tex
putting placehodlers in appendix

\begin{table}[t]
\small
\begin{center}
\begin{tabular}{|p{3in}|c|}
\hline
Architecture & $\#$ of Models \\
\hline
ResNet                                     & 30 \\
SENet/SE-ResNet/SE-PreResNet/SE-ResNeXt    & 24 \\
DIA-ResNet/DIA-PreResNet                   & 18 \\
ResNeXt                                    & 12 \\
WRN                                        & 12 \\
DLA                                        & 6 \\
PreResNet                                  & 6 \\
ProxylessNAS                               & 6 \\
VGG/BN-VGG                                 & 6 \\
IGCV3                                      & 6 \\
EfficientNet                               & 6 \\
SqueezeNext/SqNxt                          & 6 \\
ShuffleNet                                 & 6 \\
DRN-C/DRN-D                                & 6 \\
ESPNetv2                                   & 6 \\
HRNet                      z                & 6 \\
SqueezeNet/SqueezeResNet                   & 6 \\
\hline
\end{tabular}
\end{center}
\caption{Architectures used}
\label{table:architectures}
\end{table}

\begin{figure}[t]
    \centering
    \subfigure[ImageNet 1K]{
        \includegraphics[width=4.9cm]{img/all-imagenet-1k_alpha.png}
        \label{fig:imagenet1k-alpha}
    }
    \qquad
    \subfigure[ CIFAR 10 ]{
        \includegraphics[width=4.9cm]{img/all-cifar-10_alpha.png}
        \label{fig:cifar10.alpha}
    }
    \qquad
    \subfigure[ CIFAR 100 ]{
        \includegraphics[width=4.9cm]{img/all-cifar-100_alpha.png}
        \label{fig:cifar100.alpha}
    }
    \qquad
    \subfigure[ SVHN ]{
        \includegraphics[width=4.9cm]{img/all-svhn_alpha.png}
        \label{fig:svhn.alpha}
    }
    \qquad
    \subfigure[ CUB 200 ]{
        \includegraphics[width=4.9cm]{img/all-cub-200-2011_alpha.png}
        \label{fig:cub200.alpha}
    }
    \caption{% 
             %\charles{Preliminary charts:} 
             PL exponent $\alpha$ versus reported Top1 Test Accuracies for pretrained DNNs available for five different data sets.
            }
    \label{fig:DSalphas}
\end{figure}

\begin{table}[t]
\scriptsize
\begin{center}
\begin{tabular}{|c|c|c|c|c|c|}
\hline
Dataset & Model  & $\langle\log\Vert\cdot\Vert_{F}\rangle$ & $\langle\log\Vert\cdot\Vert_{\infty}\rangle$ & $\hat{\alpha}$ & $\langle\log\Vert\cdot\Vert^{\alpha}_{\alpha}\rangle$ \\
\hline
 imagenet-1k & ResNet  & 5.96 &  11.03 & \textbf{3.51} & 4.01 \\
 imagenet-1k & EfficientNet  & 2.67 &  \textbf{1.23} & 2.56 & 2.50 \\
 imagenet-1k & PreResNet  & 6.59 &  15.44 & \textbf{3.59} & 3.71 \\
 imagenet-1k & ShuffleNet  & 35.38 &  89.58 & 19.54 & \textbf{18.48} \\
 imagenet-1k & VGG  & 0.84 &  \textbf{0.68} & 1.89 & 1.59 \\
 imagenet-1k & DLA  & 22.41 &  \textbf{8.49} & 14.69 & 15.68 \\
 imagenet-1k & HRNet  & 0.47 &  0.51 & \textbf{0.16} & 0.16 \\
 imagenet-1k & DRN-C  & 0.60 &  0.66 & \textbf{0.40} & 0.48 \\
 imagenet-1k & SqueezeNext  & 21.94 &  21.39 & 13.31 & \textbf{13.23} \\
 imagenet-1k & ESPNetv2  & 13.77 &  14.74 & \textbf{1.87} & 2.53 \\
 imagenet-1k & IGCV3  & 1.94 &  87.76 & 8.48 & \textbf{1.09} \\
 imagenet-1k & ProxylessNAS  & \textbf{0.19} &  0.26 & 0.28 & 0.26 \\
 imagenet-1k & SqueezeNet  & 0.11 &  0.11 & \textbf{0.07} & 0.08 \\
\hline
 cifar-10 & ResNet  & 0.31 &  0.30 & \textbf{0.28} & 0.28 \\
 cifar-10 & DIA-ResNet  & \textbf{0.05} &  0.08 & 0.28 & 0.32 \\
 cifar-10 & SENet  & 0.09 &  0.09 & \textbf{0.04} & 0.04 \\
\hline
 cifar-100 & ResNet  & 4.13 &  4.50 & \textbf{3.06} & 3.06 \\
 cifar-100 & DIA-ResNet  & \textbf{0.36} &  1.38 & 0.93 & 1.02 \\
 cifar-100 & SENet  & 0.36 &  0.43 & \textbf{0.26} & 0.26 \\
 cifar-100 & WRN  & 0.14 &  0.20 & 0.07 & \textbf{0.06} \\
\hline
 svhn & ResNet  & 0.04 &  0.04 & \textbf{0.02} & 0.02 \\
 svhn & DIA-ResNet  & 0.00 &  \textbf{0.00} & 0.02 & 0.02 \\
 svhn & SENet  & \textbf{0.00} &  0.00 & 0.00 & 0.00 \\
 svhn & WRN  & 0.01 &  0.01 & 0.01 & \textbf{0.01} \\
 svhn & ResNeXt  & 0.00 &  \textbf{0.00} & 0.01 & 0.01 \\
\hline
 cub-200-2011 & ResNet  & 0.20 &  \textbf{0.18} & 3.19 & 3.21 \\
 cub-200-2011 & SENet  & \textbf{1.07} &  1.29 & 1.85 & 1.95 \\
\hline
\end{tabular}
\end{center}
\vspace{-5mm}
\caption{$MSE$ Results for all CV model regressions. }
\label{table:MSEresults}
\end{table}

\begin{table}[t]
\scriptsize
\begin{center}
\begin{tabular}{|c|c|c|c|c|c|}
\hline
Dataset & Model  & $\langle\log\Vert\cdot\Vert_{F}\rangle$ & $\langle\log\Vert\cdot\Vert_{\infty}\rangle$ & $\hat{\alpha}$ & $\langle\log\Vert\cdot\Vert^{\alpha}_{\alpha}\rangle$ \\
\hline
imagenet-1k & ResNet  & 0.82 &  0.67 & \textbf{0.90} & 0.88 \\
 imagenet-1k & EfficientNet  & 0.65 &  \textbf{0.84} & 0.67 & 0.67 \\
 imagenet-1k & PreResNet  & 0.73 &  0.36 & \textbf{0.85} & 0.85 \\
 imagenet-1k & ShuffleNet  & 0.63 &  0.06 & 0.80 & \textbf{0.81} \\
 imagenet-1k & VGG  & 0.71 &  \textbf{0.76} & 0.35 & 0.45 \\
 imagenet-1k & DLA  & 0.13 &  \textbf{0.67} & 0.43 & 0.39 \\
 imagenet-1k & HRNet  & 0.91 &  0.90 & \textbf{0.97} & 0.97 \\
 imagenet-1k & DRN-C  & 0.81 &  0.79 & \textbf{0.87} & 0.85 \\
 imagenet-1k & SqueezeNext  & 0.05 &  0.07 & 0.42 & \textbf{0.43} \\
 imagenet-1k & ESPNetv2  & 0.42 &  0.38 & \textbf{0.92} & 0.89 \\
 imagenet-1k & IGCV3  & 0.98 &  0.12 & 0.92 & \textbf{0.99} \\
 imagenet-1k & SqueezeNet  & 0.01 &  0.00 & \textbf{0.38} & 0.26 \\
 imagenet-1k & ProxylessNAS  & \textbf{0.68} &  0.56 & 0.53 & 0.58 \\
\hline
 cifar-10 & ResNet  & 0.58 &  0.59 & \textbf{0.62} & 0.61 \\
 cifar-10 & DIA-ResNet  & \textbf{0.96} &  0.93 & 0.74 & 0.71 \\
 cifar-10 & SENet  & 0.91 &  0.91 & \textbf{0.96} & 0.96 \\
\hline
 cifar-100 & ResNet  & 0.61 &  0.58 & \textbf{0.71} & 0.71 \\
 cifar-100 & DIA-ResNet  & \textbf{0.96} &  0.85 & 0.90 & 0.89 \\
 cifar-100 & SENet  & 0.97 &  0.96 & \textbf{0.98} & 0.98 \\
 cifar-100 & WRN  & 0.32 &  0.04 & 0.66 & \textbf{0.69} \\
\hline
 svhn & ResNet  & 0.69 &  0.70 & \textbf{0.82} & 0.81 \\
 svhn & DIA-ResNet  & 0.94 &  \textbf{0.95} & 0.78 & 0.77 \\
 svhn & SENet  & \textbf{0.99} &  0.96 & 0.98 & 0.98 \\
 svhn & WRN  & 0.13 &  0.10 & 0.20 & \textbf{0.21} \\
 svhn & ResNeXt  & 0.87 &  \textbf{0.90} & 0.64 & 0.75 \\
\hline
 cub-200-2011 & ResNet  & 0.94 &  \textbf{0.95} & 0.08 & 0.08 \\
 cub-200-2011 & SENet  & \textbf{0.66} &  0.59 & 0.41 & 0.38 \\
\hline
\end{tabular}
\end{center}
\vspace{-5mm}
\caption{$R^{2}$ Results for all CV model regressions. }
\label{table:R2results}
\end{table}

@@

To explain further how to reproduce our analysis, we run three batches of linear regressions. 
First, at the global level, we divide models by datasets and run regressions separately on all models of a certain dataset, regardless of the architecture. 
At this level, the plots are quite noisy and clustered, as each architecture has its own accuracy trend; but one can
 still see that most plots show positive relationship with positive coefficients. 
Example regressions are shown in Figure~\ref{fig:DSalphas}, as available in the results notebook.

To generate the results in Table~\ref{table:results}, we run linear regressions for each architecture series in Table~\ref{table:architectures}, regressing each empirical Log Norm metric against the reported Top1 (and Top5) errors (as listed on the \texttt{osmr/imgclsmob} github repository README file~\cite{osmr}, with the relevant data extracted and provided in our github repo as \texttt{pytorchcv.html}).
We record the $R^{2}$ and $MSE$ for each metric, averaged over all regressions for all architectures and datasets.
See Table~\ref{table:MSEresults} and Table~\ref{table:R2results}.
In the repo, plots are provided for every regression, and more fine grained results may be computed by the reader by analyzing the data in the \texttt{df\_all.xlsx} file.
The final analysis includes 108 regressions in all, those with 4 or more models, with a positive $R^2$.

>>>>

\begin{table}[t]
\small
\begin{center}
\begin{tabular}{|p{3in}|c|}
\hline
Architecture & $\#$ of Models \\
\hline
ResNet                                     & 30 \\
SENet/SE-ResNet/SE-PreResNet/SE-ResNeXt    & 24 \\
DIA-ResNet/DIA-PreResNet                   & 18 \\
ResNeXt                                    & 12 \\
WRN                                        & 12 \\
DLA                                        & 6 \\
PreResNet                                  & 6 \\
ProxylessNAS                               & 6 \\
VGG/BN-VGG                                 & 6 \\
IGCV3                                      & 6 \\
EfficientNet                               & 6 \\
SqueezeNext/SqNxt                          & 6 \\
ShuffleNet                                 & 6 \\
DRN-C/DRN-D                                & 6 \\
ESPNetv2                                   & 6 \\
HRNet                                      & 6 \\
SqueezeNet/SqueezeResNet                   & 6 \\
\hline
\end{tabular}
\end{center}
\caption{Architectures used}
\label{table:architectures}
\end{table}

\begin{figure}[t]
    \centering
    \subfigure[ImageNet 1K]{
        \includegraphics[width=4.9cm]{img/all-imagenet-1k_alpha.png}
        \label{fig:imagenet1k-alpha}
    }
    \qquad
    \subfigure[ CIFAR 10 ]{
        \includegraphics[width=4.9cm]{img/all-cifar-10_alpha.png}
        \label{fig:cifar10.alpha}
    }
    \qquad
    \subfigure[ CIFAR 100 ]{
        \includegraphics[width=4.9cm]{img/all-cifar-100_alpha.png}
        \label{fig:cifar100.alpha}
    }
    \qquad
    \subfigure[ SVHN ]{
        \includegraphics[width=4.9cm]{img/all-svhn_alpha.png}
        \label{fig:svhn.alpha}
    }
    \qquad
    \subfigure[ CUB 200 ]{
        \includegraphics[width=4.9cm]{img/all-cub-200-2011_alpha.png}
        \label{fig:cub200.alpha}
    }
    \caption{PL exponent $\alpha$ versus reported Top1 Test Accuracies for pretrained DNNs available for different datasets (as segmented in Table~\ref{table:datasets}).
            }
    \label{fig:DSalphas}
\end{figure}

\begin{figure}[t]
    \centering
    \subfigure[ ResNet ]{
        \includegraphics[width=2.7cm]{img/hex.png}
        \label{fig:ARCHalphas_01}
    }
    \subfigure[ SENet/SE-ResNet/SE-PreResNet/SE-ResNeXt ]{
        \includegraphics[width=2.7cm]{img/hex.png}
        \label{fig:ARCHalphas_02}
    }
    \subfigure[ DIA-ResNet/DIA-PreResNet ]{
        \includegraphics[width=2.7cm]{img/hex.png}
        \label{fig:ARCHalphas_03}
    }
    \subfigure[ ResNeXt ]{
        \includegraphics[width=2.7cm]{img/hex.png}
        \label{fig:ARCHalphas_04}
    }
    \subfigure[ WRN ]{
        \includegraphics[width=2.7cm]{img/hex.png}
        \label{fig:ARCHalphas_05}
    }
    \subfigure[ DLA ]{
        \includegraphics[width=2.7cm]{img/hex.png}
        \label{fig:ARCHalphas_06}
    }
    \subfigure[ PreResNet ]{
        \includegraphics[width=2.7cm]{img/hex.png}
        \label{fig:ARCHalphas_07}
    }
    \subfigure[ ProxylessNAS ]{
        \includegraphics[width=2.7cm]{img/hex.png}
        \label{fig:ARCHalphas_08}
    }
    \subfigure[ VGG/BN-VGG ]{
        \includegraphics[width=2.7cm]{img/hex.png}
        \label{fig:ARCHalphas_09}
    }
    \subfigure[ IGCV3 ]{
        \includegraphics[width=2.7cm]{img/hex.png}
        \label{fig:ARCHalphas_10}
    }
    \subfigure[ EfficientNet ]{
        \includegraphics[width=2.7cm]{img/hex.png}
        \label{fig:ARCHalphas_11}
    }
    \subfigure[ SqueezeNext/SqNxt ]{
        \includegraphics[width=2.7cm]{img/hex.png}
        \label{fig:ARCHalphas_12}
    }
    \subfigure[ ShuffleNet ]{
        \includegraphics[width=2.7cm]{img/hex.png}
        \label{fig:ARCHalphas_13}
    }
    \subfigure[ DRN-C/DRN-D ]{
        \includegraphics[width=2.7cm]{img/hex.png}
        \label{fig:ARCHalphas_14}
    }
    \subfigure[ ESPNetv2 ]{
        \includegraphics[width=2.7cm]{img/hex.png}
        \label{fig:ARCHalphas_15}
    }
    \subfigure[ HRNet ]{
        \includegraphics[width=2.7cm]{img/hex.png}
        \label{fig:ARCHalphas_16}
    }
    \subfigure[ SqueezeNet/SqueezeResNet ]{
        \includegraphics[width=2.7cm]{img/hex.png}
        \label{fig:ARCHalphas_17}
    }
    \caption{PL exponent $\alpha$ versus reported Top1 Test Accuracies for pretrained DNNs available for different architecture series (as segmented in Table~\ref{table:architectures}).
            }
    \label{fig:ARCHalphas}
\end{figure}

\begin{table}[t]
\scriptsize
\begin{center}
\begin{tabular}{|c|c|c|c|c|c|}
\hline
Dataset & Model  & $\langle\log\Vert\cdot\Vert_{F}\rangle$ & $\langle\log\Vert\cdot\Vert_{\infty}\rangle$ & $\hat{\alpha}$ & $\langle\log\Vert\cdot\Vert^{\alpha}_{\alpha}\rangle$ \\
\hline
 imagenet-1k & ResNet  & 5.96 &  11.03 & \textbf{3.51} & 4.01 \\
 imagenet-1k & EfficientNet  & 2.67 &  \textbf{1.23} & 2.56 & 2.50 \\
 imagenet-1k & PreResNet  & 6.59 &  15.44 & \textbf{3.59} & 3.71 \\
 imagenet-1k & ShuffleNet  & 35.38 &  89.58 & 19.54 & \textbf{18.48} \\
 imagenet-1k & VGG  & 0.84 &  \textbf{0.68} & 1.89 & 1.59 \\
 imagenet-1k & DLA  & 22.41 &  \textbf{8.49} & 14.69 & 15.68 \\
 imagenet-1k & HRNet  & 0.47 &  0.51 & \textbf{0.16} & 0.16 \\
 imagenet-1k & DRN-C  & 0.60 &  0.66 & \textbf{0.40} & 0.48 \\
 imagenet-1k & SqueezeNext  & 21.94 &  21.39 & 13.31 & \textbf{13.23} \\
 imagenet-1k & ESPNetv2  & 13.77 &  14.74 & \textbf{1.87} & 2.53 \\
 imagenet-1k & IGCV3  & 1.94 &  87.76 & 8.48 & \textbf{1.09} \\
 imagenet-1k & ProxylessNAS  & \textbf{0.19} &  0.26 & 0.28 & 0.26 \\
 imagenet-1k & SqueezeNet  & 0.11 &  0.11 & \textbf{0.07} & 0.08 \\
\hline
 cifar-10 & ResNet  & 0.31 &  0.30 & \textbf{0.28} & 0.28 \\
 cifar-10 & DIA-ResNet  & \textbf{0.05} &  0.08 & 0.28 & 0.32 \\
 cifar-10 & SENet  & 0.09 &  0.09 & \textbf{0.04} & 0.04 \\
\hline
 cifar-100 & ResNet  & 4.13 &  4.50 & \textbf{3.06} & 3.06 \\
 cifar-100 & DIA-ResNet  & \textbf{0.36} &  1.38 & 0.93 & 1.02 \\
 cifar-100 & SENet  & 0.36 &  0.43 & \textbf{0.26} & 0.26 \\
 cifar-100 & WRN  & 0.14 &  0.20 & 0.07 & \textbf{0.06} \\
\hline
 svhn & ResNet  & 0.04 &  0.04 & \textbf{0.02} & 0.02 \\
 svhn & DIA-ResNet  & 0.00 &  \textbf{0.00} & 0.02 & 0.02 \\
 svhn & SENet  & \textbf{0.00} &  0.00 & 0.00 & 0.00 \\
 svhn & WRN  & 0.01 &  0.01 & 0.01 & \textbf{0.01} \\
 svhn & ResNeXt  & 0.00 &  \textbf{0.00} & 0.01 & 0.01 \\
\hline
 cub-200-2011 & ResNet  & 0.20 &  \textbf{0.18} & 3.19 & 3.21 \\
 cub-200-2011 & SENet  & \textbf{1.07} &  1.29 & 1.85 & 1.95 \\
\hline
\end{tabular}
\end{center}
\vspace{-5mm}
\caption{$MSE$ results for our analysis of all CV models in Table~\ref{table:datasets}. }
\label{table:MSEresults}
\end{table}

\begin{table}[t]
\scriptsize
\begin{center}
\begin{tabular}{|c|c|c|c|c|c|}
\hline
Dataset & Model  & $\langle\log\Vert\cdot\Vert_{F}\rangle$ & $\langle\log\Vert\cdot\Vert_{\infty}\rangle$ & $\hat{\alpha}$ & $\langle\log\Vert\cdot\Vert^{\alpha}_{\alpha}\rangle$ \\
\hline
imagenet-1k & ResNet  & 0.82 &  0.67 & \textbf{0.90} & 0.88 \\
 imagenet-1k & EfficientNet  & 0.65 &  \textbf{0.84} & 0.67 & 0.67 \\
 imagenet-1k & PreResNet  & 0.73 &  0.36 & \textbf{0.85} & 0.85 \\
 imagenet-1k & ShuffleNet  & 0.63 &  0.06 & 0.80 & \textbf{0.81} \\
 imagenet-1k & VGG  & 0.71 &  \textbf{0.76} & 0.35 & 0.45 \\
 imagenet-1k & DLA  & 0.13 &  \textbf{0.67} & 0.43 & 0.39 \\
 imagenet-1k & HRNet  & 0.91 &  0.90 & \textbf{0.97} & 0.97 \\
 imagenet-1k & DRN-C  & 0.81 &  0.79 & \textbf{0.87} & 0.85 \\
 imagenet-1k & SqueezeNext  & 0.05 &  0.07 & 0.42 & \textbf{0.43} \\
 imagenet-1k & ESPNetv2  & 0.42 &  0.38 & \textbf{0.92} & 0.89 \\
 imagenet-1k & IGCV3  & 0.98 &  0.12 & 0.92 & \textbf{0.99} \\
 imagenet-1k & SqueezeNet  & 0.01 &  0.00 & \textbf{0.38} & 0.26 \\
 imagenet-1k & ProxylessNAS  & \textbf{0.68} &  0.56 & 0.53 & 0.58 \\
\hline
 cifar-10 & ResNet  & 0.58 &  0.59 & \textbf{0.62} & 0.61 \\
 cifar-10 & DIA-ResNet  & \textbf{0.96} &  0.93 & 0.74 & 0.71 \\
 cifar-10 & SENet  & 0.91 &  0.91 & \textbf{0.96} & 0.96 \\
\hline
 cifar-100 & ResNet  & 0.61 &  0.58 & \textbf{0.71} & 0.71 \\
 cifar-100 & DIA-ResNet  & \textbf{0.96} &  0.85 & 0.90 & 0.89 \\
 cifar-100 & SENet  & 0.97 &  0.96 & \textbf{0.98} & 0.98 \\
 cifar-100 & WRN  & 0.32 &  0.04 & 0.66 & \textbf{0.69} \\
\hline
 svhn & ResNet  & 0.69 &  0.70 & \textbf{0.82} & 0.81 \\
 svhn & DIA-ResNet  & 0.94 &  \textbf{0.95} & 0.78 & 0.77 \\
 svhn & SENet  & \textbf{0.99} &  0.96 & 0.98 & 0.98 \\
 svhn & WRN  & 0.13 &  0.10 & 0.20 & \textbf{0.21} \\
 svhn & ResNeXt  & 0.87 &  \textbf{0.90} & 0.64 & 0.75 \\
\hline
 cub-200-2011 & ResNet  & 0.94 &  \textbf{0.95} & 0.08 & 0.08 \\
 cub-200-2011 & SENet  & \textbf{0.66} &  0.59 & 0.41 & 0.38 \\
\hline
\end{tabular}
\end{center}
\vspace{-5mm}
\caption{$R^{2}$ results for our analysis of all CV models in Table~\ref{table:datasets}. }
\label{table:R2results}
\end{table}

\begin{table}[t]
\scriptsize
\begin{center}
\begin{tabular}{|c|c|c|c|c|c|}
\hline
Dataset & Model  & $\langle\log\Vert\cdot\Vert_{F}\rangle$ & $\langle\log\Vert\cdot\Vert_{\infty}\rangle$ & $\hat{\alpha}$ & $\langle\log\Vert\cdot\Vert^{\alpha}_{\alpha}\rangle$ \\
\hline
 imagenet-1k  & ResNet        &  XXX &   XXX &  XXX &  XXX \\
 imagenet-1k  & EfficientNet  &  XXX &   XXX &  XXX &  XXX \\
 imagenet-1k  & PreResNet     &  XXX &   XXX &  XXX &  XXX \\
 imagenet-1k  & ShuffleNet    &  XXX &   XXX &  XXX &  XXX \\
 imagenet-1k  & VGG           &  XXX &   XXX &  XXX &  XXX \\
 imagenet-1k  & DLA           &  XXX &   XXX &  XXX &  XXX \\
 imagenet-1k  & HRNet         &  XXX &   XXX &  XXX &  XXX \\
 imagenet-1k  & DRN-C         &  XXX &   XXX &  XXX &  XXX \\
 imagenet-1k  & SqueezeNext   &  XXX &   XXX &  XXX &  XXX \\
 imagenet-1k  & ESPNetv2      &  XXX &   XXX &  XXX &  XXX \\
 imagenet-1k  & IGCV3         &  XXX &   XXX &  XXX &  XXX \\
 imagenet-1k  & SqueezeNet    &  XXX &   XXX &  XXX &  XXX \\
 imagenet-1k  & ProxylessNAS  &  XXX &   XXX &  XXX &  XXX \\
\hline
 cifar-10     & ResNet        &  XXX &   XXX &  XXX &  XXX \\
 cifar-10     & DIA-ResNet    &  XXX &   XXX &  XXX &  XXX \\
 cifar-10     & SENet         &  XXX &   XXX &  XXX &  XXX \\
\hline
 cifar-100    & ResNet        &  XXX &   XXX &  XXX &  XXX \\
 cifar-100    & DIA-ResNet    &  XXX &   XXX &  XXX &  XXX \\
 cifar-100    & SENet         &  XXX &   XXX &  XXX &  XXX \\
 cifar-100    & WRN           &  XXX &   XXX &  XXX &  XXX \\
\hline
 svhn         & ResNet        &  XXX &   XXX &  XXX &  XXX \\
 svhn         & DIA-ResNet    &  XXX &   XXX &  XXX &  XXX \\
 svhn         & SENet         &  XXX &   XXX &  XXX &  XXX \\
 svhn         & WRN           &  XXX &   XXX &  XXX &  XXX \\
 svhn         & ResNeXt       &  XXX &   XXX &  XXX &  XXX \\
\hline
 cub-200-2011 & ResNet        &  XXX &   XXX &  XXX &  XXX \\
 cub-200-2011 & SENet         &  XXX &   XXX &  XXX &  XXX \\
\hline
\end{tabular}
\end{center}
\vspace{-5mm}
\caption{Kendall-$\tau$ results for our analysis of all CV models in Table~\ref{table:datasets}. }
\label{table:KTresults}
\end{table}

@@

\michael{The text in this section needs to be changed---probably not removed, but instead discuss things, not point to the figure we remove, and point to the repo. }

\michael{Do we get more visually compelling results if we present figures, but segmented by architectures, as listed in Table~\ref{table:architectures}; if so, perhaps we should put those, so we don't tell R1 that we just removed what looked bad; or maybe actually both, since we segment by dataset in Table~\ref{table:datasets}. }

To explain further how to reproduce our analysis, we run three batches of linear regressions. 
First, at the global level, we divide models by datasets and run regressions separately on all models of a certain dataset, regardless of the architecture. 
At this level, the plots are quite noisy and clustered, as each architecture has its own accuracy trend; but one can
 still see that most plots show positive relationship with positive coefficients. 
% V1 REMOVED FOR V2 % Example regressions are shown in Figure~\ref{fig:DSalphas}, as available in the results notebook.
Example regressions are shown in 
Figure~\ref{fig:DSalphas}, for models segmented by dataset, as listed in Table~\ref{table:datasets}, 
and in 
Figure~\ref{fig:ARCHalphas}, for models segmented by architecture, as listed in Table~\ref{table:architectures}.
\michael{Comment here on differences.}

To generate the results in Table~\ref{table:results}, we run linear regressions for each architecture series in Table~\ref{table:architectures}, regressing each empirical Log Norm metric against the reported Top1 (and Top5) errors (as listed on the \texttt{osmr/imgclsmob} github repository README file~\cite{osmr}, with the relevant data extracted and provided in our github repo as \texttt{pytorchcv.html}).
We record the $R^{2}$ and $MSE$ for each metric, averaged over all regressions for all architectures and datasets.
See Table~\ref{table:MSEresults}, Table~\ref{table:R2results}, and Table~\ref{table:KTresults}.
In the repo, plots are provided for every regression, and more fine grained results may be computed by the reader by analyzing the data in the \texttt{df\_all.xlsx} file.
The final analysis includes 108 regressions in all, those with 4 or more models, with a positive $R^2$.
